Catchy Title Goes Here

### 2018-04-30 Paper/paper.tex
small revisions

In situations in which vaccination is present, vaccination provides a second means of acquiring immunity - the `force of vaccination,' or `vaccination hazard.' If we represent this as $v(a)$, then we can extend Eq.~\ref{eq:CatMod} to give the probability of an individual testing seropositive at age $a$ as
\begin{align}
p(\mathrm{immune}|a)  &= 1 - \exp\left( - \int_0^a f(a') + v(a') da'\right) \nonumber \\ 
&=1 - \exp\left(-\int_0^a f(a') - \int_0^a v(a') da'\right).
\label{eq:CatModSum}
\end{align}

@@

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Results:
Simulation experiment ? illustrate for 10 levels of vaccine effectiveness:
	a) Does fitted model using vaccination and case data only recover the true seroprevalence?
	b) Need to show that it recovers the vaccination hazard as well
	c) show estimate of vaccine effectiveness
Figure 1 ? 3-panel figure illustrating those 3 points

>>>>

In situations in which vaccination is present, vaccination provides a second means of acquiring immunity - the `force of vaccination,' or `vaccination hazard' (vh). If we represent this as $v(a)$, then we can extend Eq.~\ref{eq:CatMod} to give the probability of an individual testing seropositive at age $a$ as
\begin{align}
p(\mathrm{immune}|a)  &= 1 - \exp\left( - \int_0^a f(a') + v(a') da'\right) \nonumber \\ 
&=1 - \exp\left(-\int_0^a f(a') - \int_0^a v(a') da'\right).
\label{eq:CatModSum}
\end{align}

@@

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Although we have chosen a flexible functional form to represent the force of infection and vaccination hazards, we know that that the true functions present in nature are unlikely to be precisely matched by Weibull distributions. This will necessarily lead to some level of biases in our inferences. To understand these possible biases, we analyze simulated data with known foi, vh, and $\gamma$ (vaccine efficacy), and examine the results.  
Results:
Simulation experiment ? illustrate for 10 levels of vaccine effectiveness:
	a) Does fitted model using vaccination and case data only recover the true seroprevalence?
	b) Need to show that it recovers the vaccination hazard as well
	c) show estimate of vaccine effectiveness
Figure 1 ? 3-panel figure illustrating those 3 points
